Trans-dimensional Bayesian Inference and Nested Sampling

### 2015-02-02 Documents/Talk/content.tex
Amplitudes comment
More figures

@@

\begin{frame}[t]{Recommendations}
It is infeasible to apply this approach wholesale.
Instead I would use it on small subsets of imaging that are of specific interest.

@@

>>>>

\begin{frame}[t]{Motivating Problem I}
\begin{itemize}
\item How many sinusoids are in this data?
\item {\it Note that this must depend on what we believe about their properties,
particularly the amplitudes}
\end{itemize}
\begin{center}
\includegraphics[scale=0.35]{sinewave_data.pdf}
\end{center}
\end{frame}

@@

\begin{frame}[t]{Recommendations}
It is infeasible to apply this approach wholesale (i.e. to a whole survey).
Instead I would use it on very small subsets of imaging that are of specific
interest.

@@

\begin{frame}[t]{Gliese 581 -- Number of Signals}
\begin{center}
\includegraphics[scale=0.35]{ExoplanetFigures/gliese581_N.pdf}
\end{center}
\end{frame}

\begin{frame}[t]{Gliese 581 -- Periods}
\begin{center}
\includegraphics[scale=0.4]{ExoplanetFigures/gliese581_periods.pdf}
\end{center}
\end{frame}

\begin{frame}[t]{Gliese 581 -- Model Fit (Part of Dataset)}
\begin{center}
\includegraphics[scale=0.4]{ExoplanetFigures/gliese581.pdf}
\end{center}
\end{frame}

\begin{frame}[t]{Gliese 581 -- Likelihood vs Enclosed Prior Mass}
\begin{center}
\includegraphics[scale=0.4]{ExoplanetFigures/logl.pdf}
\end{center}
\end{frame}
